Behaviour Analysis Report
========================================================

Todo : add content

Introduction
------------------------
This analysis report is generated using R, R-studio and knitr to knitr R code from markdown into html and later LateX format. We have the option to include all R code that is used to generate the plots and calculations. Default this feauture is dissabled.
The behaviour analysis step is the second step in a datamining analysis.
Steps identified in the datamining process are: 
* Data analysis 
* Behaviour analysis 
* Missing value analysis 
* Missing value imputation (optional) 
* Binning 
* Feature selection 
* Model development 
* Model analysis 
* Model deployment

Information on Dataset 
------------------------------------
Basic information from the dataset we are using.

```{r eval=TRUE, echo=FALSE}
# set global chunk options 
opts_chunk$set(echo=FALSE, cache=FALSE, tidy=TRUE, warning=FALSE, error=TRUE)
# read externalized R from R script
read_chunk("behaviour-analysis-template.R")
```


```{r read_data}

```
We are using data from file : `r filename`
The dataset has `r colums` variables and `r rows` rows.

Variabele types
-----------------------------
```{r var_types}

```
The following variabeles are present in the dataset:
`r var_names` 

We have `r num_vars` numeric variables and `r cat_vars` categorical variables (or factors in R).

