
```{r load_pander_methods, results='hide', echo=FALSE}
require(knitr)
opts_chunk$set(echo=FALSE,message=FALSE,results = 'asis',comment=NA)

print(3)

require(pander)
replace.print.methods <- function(PKG_name = 'pander') {
  PKG_methods <- as.character(methods(PKG_name))
  print_methods <- gsub(PKG_name, 'print', PKG_methods)
  for(i in seq_along(PKG_methods)) {
    f <- eval(parse(text=paste(PKG_name,':::', PKG_methods[i], sep = '')))
    assign(print_methods[i], f, '.GlobalEnv')
  }   
}
replace.print.methods()
```


# Introduction

The dataMineR script toolbox aims to be a efficient set of R \& knitr scripts, 
that can be used by experienced and less experience dataminers. 
The toolbox uses the best of the R community to efficently analayse any arbritray dataset 
and make a predictive model on the target variable.
The toolbox uses R ``version$version.string``}, 
R-studio and knitr(http://yihui.name/knitr/) to knit R code 
and Latex into nice and readable pdf reports. 
We have the option to include all R code that is used to generate the plots and calculations 
(see "chunk\_options"). By default this feauture is dissabled.

# CRoss Industry Standard Process for datamining

In this toolkit we will use the CRISP methodology to guide the datamining proces.



Doc header 1
============
Some text explaining the analysis we are doing

```{r comment=NA}
lm(mpg ~ wt, data = mtcars)
summary(cars)# a summary table
fit <- lm(dist~speed, data = cars)
fit
plot(cars) # a plot
```



-------
This report was generated with [R](http://www.r-project.org/) (2.15.2) and [pander](https://github.com/rapporter/pander) (0.3.1) on x86_64-apple-darwin9.8.0 platform.