Data Analysis Report
========================================================

Todo : add table of content

Introduction
------------------------
This data analysis report is generated using R-studio and knitr to knit R code and markdown into html format. We have the option to include all R code that is used to generate the plots and calculations. Default this feauture is dissabled.
The data analysis step is the first step an a datamining analysis.

Dataset Basic Artifacts 
------------------------------------
Basic information from the dataset we are using.

### Basic dataset information

```{r eval=TRUE, echo=FALSE}
# set global chunk options 
opts_chunk$set(echo=FALSE, cache=FALSE, tidy=TRUE, warning=FALSE, error=TRUE)
# read externalized R from R script
read_chunk("data-analysis.R")
```


```{r read_data}

```
We are using data from file : `r filename`
The dataset has `r colums` variables and `r rows` rows.  

The case identifyer is *`r original_case_id`* this is unique for all cases.

Variabele types
-----------------------------
```{r var_types}

```
The following variabeles are present in the dataset:
`r var_names` 

We have `r num_vars` numeric variables and `r cat_vars` categorical variables (or factors in R).


Excluded variables
------------------------------
From the varables provided the folowing list will be excluded in this anlysis: ```r exclude_var_names```

Sometimes categoric variables are present as coded numbers. These should be treated as factors.
In this dataset the following variables will be used as factors(categoric): ```r treat_as_categorical```

We have ```r num_vars``` numeric variables and ```r cat_vars``` categorical variables (or factors in R).

Numeric variables
=============================
Here we analyse all numeric variables. We start with an overview on basic statistics per variable. We check for missing values. We do a histogram plot to show the distribution for this variable. And we test for outliers.


Overview
-----------------------------
In the table below we report the number of observations (n), the smallest observation (min),  the first quantile (q1), the media ,  the mean, last quantile, the largest observation (max), and the nber of missing values (na).

```{r num-overview-md, results='asis'}

```

 
