% Data Analysis Report
% dataMineR
% 18/6/2013


Introduction
============

This data analysis report is generated using R-studio and knitr to knit R code and markdown into html format. We have the option to include all R code that is used to generate the plots and calculations. Default this feauture is dissabled.
The data analysis step is the first step an a datamining analysis.

Dataset Basic Artifacts 
-----------------------

Basic information from the dataset we are using.

```{r setup, echo=FALSE, cache=FALSE}
# set global chunk options APPERENTLY CANNOT BE EXTERNALIZED
opts_chunk$set(echo=FALSE, cache=FALSE, tidy=TRUE, warning=false, message=FALSE,error=TRUE)
# read externalized R from R script
read_chunk("data-analysis.R")
```

```{r read_data, echo=TRUE, cache=FALSE}

```
We are using data from file: `r path2file`. The dataset has `r colums` variables and `r rows` rows. 

The case identifyer is *`r original_case_id`* this is unique for all cases.


Variabele types
---------------

```{r var_types }

```

The following variabeles are present in the dataset: `r var_names` 

We have `r num_vars` numeric variables and `r cat_vars` categorical variables (or factors in R).


Excluded variables
------------------

From the varables provided the folowing list will be excluded in this anlysis: `r exclude_var_names`

Sometimes categoric variables are present as coded numbers. These should be treated as factors.
In this dataset the following variables will be used as factors(categoric): `r treat_as_categorical`

We have `r num_vars` numeric variables and `r cat_vars` categorical variables (or factors in R).


Numeric variables
=================

Here we analyse all numeric variables. We start with an overview on basic statistics per variable. We check for missing values. We do a histogram plot to show the distribution for this variable. And we test for outliers.


Overview
--------

In the table below we report the number of observations (n), the smallest observation (min),  the first quantile (q1), the media ,  the mean, last quantile, the largest observation (max), and the nber of missing values (na).

```{r num-overview-md, results='asis'}

```

```{r run-numeric-md, include=FALSE}
out = NULL
for (i in c(1:num_vars)) {
  out = c(out, knit_child('da-numeric.Rmd'))
}
```
`r paste(out, collapse = '\n')`


Categorical variables
======================================
Here we analyse all categorical variables. We first check the number of different levels in each category(or factor). Then we do a bar plot to show the distribution for each variable.  

Overview
--------------------------------------
In the following table we will see each variable printed with it's unique levels. Beside each level a count is made and a precentage calculated. In the last colum we find a culumative count summing the total up to 100\%. 

```{r cat-overview, results='tex'}

```

We see that the number of levels can be quite big, for reporting we will omit all variables with more then  `r max_levels` levels. These will not be reported in the subsections below.
```{r cat-levels-md, results='asis'}

```

Variables with to many levels to report are : `r c_var_names.not_reported` .  

```{r run-categoric-md, include=FALSE}

```

`r paste(out, collapse = '\n')`

Behavioural Analysis
==================================
The next step is behavioural analysis.
The current dataset is now saved.
```{r save-data}

```

Dataset saved as : `r datasetName`

